\begin{centering}
\textbf{ACKNOWLEDGMENTS}\\
\vspace{\baselineskip}
\end{centering}

I have been in the United States for seven years and in the quiet and beautiful down of Bloomington, Indiana for five years to accomplish this doctoral program. I have never imagine that time can go that fast. Being a scientist was my dream when I was a child, it is so excited for me to be so close to reach it now. Doctoral life is long and mixed with depression and pressure, while it also associated with the happiness when my sweat irrigates published papers. I am really glad that I can achieve something before my thirty-year old birthday. 

Thank my advisor, Xiaozhong Liu, who patiently brings me from nobody to a guy with certified academic and industrial experiences. I will always follow his edification throughout my future career  and try my best to be outstanding. Also big thanks to all my committee members to offer me supportive suggestions about how to criticize researches, draft papers and present works. 

Thank my parents and girlfriend who support me since the very beginning of my study aboard. I barely have time and opportunity  to accompany with them due to the long long distance from the United States to China. Their comprehension is my solid back-support to overcome all challenges occurred in these years.

Thank all colleagues I met during my two internships at Alibaba and Amazon. I was inspired so much from these talented people in terms of how to do academic researches and be professional in industry. Hanging out with them upgrades myself significantly. 

Finally, I hope the pandemic can be gone soon and people can restart their works. I am so grateful for what I have and can't bear to lose anything more from the pandemic. Truly wish a peaceful world without suffering any pain. 