\chapter*{Curriculum Vitae}
\addtocontents{toc}{
 \unexpanded{\unexpanded{\renewcommand{\cftchapdotsep}{\cftnodots}}}%  
}
\pagenumbering{gobble}
\addcontentsline{toc}{chapter}{Curriculum Vitae} 
%\doublespacing
\begin{spacing}{1.0}
	%%行间距变为single-space


\begin{cv}{}
	\begin{cvlist}{Education}
		\item[08/2015--06/2020] \textbf{Ph.D. in Information Science} \\ Indiana University Bloomington, USA
		\item[08/2013--05/2015] \textbf{Master in Information Science}\\ University of Pittsburgh, USA
		\item[08/2009--05/2013] \textbf{Bachelor in Information Management and System} \\ Shanghai International Studies University, China
	\end{cvlist}

	\begin{cvlist}{Industry Experience}
	\item[06/2019--09/2019] Data Scientist Intern, Amazon Alexa AI, USA 
	\item[02/2018--03/2019] NLP research Intern, Alibaba DAMO Academy, China
	\end{cvlist}

	\begin{cvlist}{Teaching Experience}
		\item[01/2018--12/2019] Instructor / Lecturer, Indiana University Bloomington, USA
	\item[08/2015--12/2017] Associate Instructor, Indiana University Bloomington, USA
	\end{cvlist}
	
	\begin{cvlist}{Publication}
		\item \textbf{Zheng Gao}, Hongsong Li, Zhuoren Jiang, Xiaozhong Liu. Detecting User Community in Sparse Domain via Cross-Graph Pairwise Learning. \textit{ACM SIGIR Conference on Research and Development in Information Retrieval (SIGIR)}, 2020.
		 \item \textbf{Zheng Gao}, Lujun Zhao, Heng Huang, Hongsong Li, Changlong Sun, Luo Si, Xiaozhong Liu. Behavior based Dynamic Summarization on Product Aspects via Reinforcement Neighbour Selection. \textit{European Conference on Artificial Intelligence (ECAI)}, 2020.
		\item Zhuoren Jiang, \textbf{Zheng Gao}, Jinjiong Lan, Hongxia Yang, Yao Lu and Xiaozhong Liu. Task-Oriented Genetic Activation for Large-Scale Complex Heterogeneous Graph Embedding. \textit{The Web Conference (WWW)}, 2020.
		\item \textbf{Zheng Gao}, Chun Guo, Xiaozhong Liu. Efficient Personalized Community Detection via Genetic Evolution. \textit{The Genetic and Evolutionary Computation Conference (GECCO)}, 2019.
		\item \textbf{Zheng Gao}, Gang Fu, Chunping Ouyang, Satoshi Tsutsui, Xiaozhong Liu, Jeremy Yang, Christopher Gessner, Brian Foote, David Wild, Ying Ding, Qi Yu. edge2vec: Representation Learning Using Edge Semantics for Biomedical Knowledge Discovery. \textit{BMC Bioinformatics}, 2019. (impact factor = 2.511).
		\item Yongzhen Wang, Xiaozhong Liu, \textbf{Zheng Gao}. Neural Related Work Summarization with a Joint Context-driven Attention Mechanism. \textit{Conference on Empirical Methods in Natural Language Processing (EMNLP)}, 2018.
		\item Zizhe Gao, \textbf{Zheng Gao}, Heng Huang, Zhuoren Jiang, Yuliang Yan. An End-to-end Model of Predicting Diverse Ranking On Heterogeneous Feeds. \textit{eCOM Workshop at ACM SIGIR Conference on Research and Development in Information Retrieval (eCom-SIGIR)}, 2018.
		\item \textbf{Zheng Gao}, Lin Guo, Chi Ma, Xiao Ma, Kai Sun, Hang Xiang, Xiaoqiang Zhu, Hongsong Li, Xiaozhong Liu. AMAD: Adversarial Multiscale Anomaly Detection on High-Dimensional and Time-Evolving Categorical Data. \textit{Deep Learning Practice for High-Dimensional Sparse Data Workshop at ACM SIGKDD Conference on Knowledge Discovery and Data Mining (DLP-KDD)}, 2019.
		\item Zhuoren Jiang, Liangcai Gao, Ke Yuan, \textbf{Zheng Gao}, Zhi Tang, Xiaozhong Liu. Mathematics Content Understanding for Cyberlearning via Formula Evolution Map. \textit{ACM International Conference on Information and Knowledge Management (CIKM)}, 2018.
		\item Xiaozhong Liu, Xing Yu, \textbf{Zheng Gao}, Tian Xia, Johan Bollen. Comparing Community-based Information Adoption and Diffusion across Different Microblogging Sites. \textit{ACM Conference on Hypertext and Social Media}, 2016.
		\item \textbf{Zheng Gao}, Vincent Malic, Shutian Ma, Patrick Shih. How to Make a Successful Movie: Factor Analysis from both Financial and Critical Perspectives. \textit{International Conference on Information}, 2019.
		\item Yongzhen Wang, Yan Lin, \textbf{Zheng Gao}, Yan Chen. A Two-stage Iterative Approach to Improve Crowdsourcing-based Relevance Assessment. \textit{Arabian Journal for Science and Engineering}, 2019.
		\item \textbf{Zheng Gao}, John Wolohan, Fast NLP-based Pattern Matching in Real Time Tweet Recommendation. \textit{Text REtrieval Conference (TREC)}, 2017.
		\item \textbf{Zheng Gao}, Rui Bi. University of Pittsburgh at TREC 2014 Microblog Track. 
		\textit{Text REtrieval Conference (TREC)}, 2014.
		\item \textbf{Zheng Gao}, Xiaozhong Liu. Personalized Community Detection in Scholarly Network. \textit{International Conference on Information}, 2017.
		\item Tian Xia, Xing Yu, \textbf{Zheng Gao}, Yijun Gu, Xiaozhong Liu. Internal/External Information Access and Information Diffusion in Social Media. \textit{International Conference on Information}, 2017.
		\item Nan Li, Naren Suri, \textbf{Zheng Gao}, Tian Xia, Xiaozhong Liu, Katy Borner. Enter a Job, Get Course Recommendations. \textit{International Conference on Information}, 2017.
		
		\item Chenwei Zhang, \textbf{Zheng Gao}, Xiaozhong Liu. How Others Affect Your Twitter \#hashtag Adoption? Examination of Community-based and Context-based Information Diffusion in Twitter. \textit{International Conference on Information}, 2015. 
		\item \textbf{Zheng Gao}, Patrick C. Shih. Communities of Support: Social Support Discussion in a HIV Online Forum. \textit{International Symposium of Chinese CHI}, 2019.
		\item Satoshi Tsutsui, \textbf{Zheng Gao}, Yuzhuo Wang, Guilin Meng, Ying Ding. A Case Study on Viziometrics: What’s the Role of Western Blots in Alzheimer’s Disease Literature. \textit{International Conference on Information}, 2018.
	\end{cvlist}
	
\date{}
\end{cv}
\end{spacing}
\pagenumbering{gobble}