\chapter{Introduction}
focus on community detection. introduce the overall development in the recent decade and particularly address three subtle tasks.


summary or empirical studies.
graph types: heterogeneous, directed, weighted, sparse, temporal(time involving), hyper graph,multi-layer,large scale
different tasks: math proof (threshold), overlapping, number of communities, top-k community search// subgraph, Enhancing community detection, semi-supervised community detection
applications: biology, citation analysis, transportation, social network
methods: Modularity, Spectral, Stochastic block model,  deep learning, nmf,Multiscale (hierarchical), multi-view, with enriched information, community recovery, flow based(random walk), link based, motif, others
challenges: resolution limit, unbalanced groups,
evaluation, software, datasets


so far community detection is more like a statistic/ physics questions instead of computer science and arificial intelligence question. 
modularity -> sbm -> deep learning. modularity and sbm are more clear tasks. deep learning methods are fuzzy.
spectral clustering all the time


future tracks: from computer science perspective, deep learning, random graph? hyper graph? multiscale?

findings: biology has delay, not easy to get a lot citations in short time.

concept level difference between subgraph, community, motif, cliques: community is from node side, others are from graph side. it is a part of community search.

overlapping has huge correlation with nmf
spetral clustering and sbm are highly correlated

some tracks are huge: modularity (newman), stochastic block model (newman) and overlapping (Jure)

try my best to distinguish each category, but there are still some overlaps between them. Some algorithms are both for overlapping community detection using deep learning techniques.

mention other types of approaches a bit, such as link community detection, 

summarize some trend, well known professor/teams, by years. which venue tends to be more popular.

I manually code five hundred most influential papers in community detection domain.
\cite{newman2012communities}
\input{chapter1/chapter1.1.tex}
\input{chapter1/chapter1.2.tex}
\input{chapter1/chapter1.3.tex}
\input{chapter1/chapter1.4.tex}
\input{chapter1/chapter1.5.tex}

